Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-09-29 paper-2024-sac-marl-neighbouring-strategies.tex
chore: add concept
chore: fix the compile error
anonymized paper
rephrase abstract

\author{Nicolò Malucelli}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{University of Bologna}
  \streetaddress{Via dell'Università, 50}
  \city{Cesena} 
  \country{Italy}
}
\email{nicolò.malucelli@studio.unibo.it}

\author{Davide Domini}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{University of Bologna}
  \streetaddress{Via dell'Università, 50}
  \city{Cesena} 
  \country{Italy}
}
\email{davide.domini@unibo.it}

\author{Gianluca Aguzzi}
\affiliation{%
  \institution{University of Bologna}
  \streetaddress{Via dell'Università, 50}
  \city{Cesena} 
  \country{Italy}
}
\email{gianluca.aguzzi@unibo.it}

\author{Mirko Viroli}
\affiliation{%
  \institution{University of Bologna}
  \streetaddress{Via dell'Università, 50}
  \city{Cesena} 
  \country{Italy}
}
\email{mirko.viroli@unibo.it}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{N. Malucelli et al.}

\begin{abstract}
  Multi-Agent Reinforcement Learning (MARL) is gaining popularity as a powerful framework for training agents to collaborate and compete in complex environments. However, MARL introduces unique challenges, such as non-stationarity and partial observability, that complicate the training process.  
  While centralized training methods can address some of these challenges, they often face scalability limitations as the number of agents grows. This paper investigates the effectiveness of various neighbor-based decentralized training strategies as a viable alternative to centralized training. We evaluate Experience Sharing, Nearest Neighboring Averaging, and Nearest Neighboring Consensus methods in a custom multi-agent environment and compare their performance against centralized training. Our results show that neighbor-based methods can achieve comparable performance to centralized training while offering improved scalability and communication efficiency. 
  We discuss the trade-offs between these methods and provide insights into their applicability in different scenarios.
  %% More -- add the fact that this make it possible to train agents in a decentralized manner, which is more realistic and scalable than centralized training.
\end{abstract}
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

@@

\section{Neighboring-Based Distributed Learning Strategies}
\begin{itemize}
\item Provide a detailed explanation of each neighbor-based method:
\begin{itemize}
\item \textbf{Independent learners:} Emphasize its simplicity and scalability but highlight its vulnerability to non-stationarity.
\item \textbf{NN-Averaging:} Describe the weight averaging process, discuss the influence of neighbor selection and averaging frequency, and mention weighted averaging variations.
\item \textbf{NN-Consensus:} Explain the selection of the best-performing network and its potential benefits and drawbacks.
\item \textbf{Experience Sharing:} Detail how agents share experiences, discuss asynchronous vs. synchronous sharing, and highlight its advantages in sparse interaction environments.
\end{itemize}
\end{itemize}

\section{Experimental Setup}
\begin{itemize}
\item Introduce the custom "collect the items" multi-agent environment:
\begin{itemize}
\item Describe the environment's dynamics, agent goals, and challenges.
\item Specify the action space (continuous and discrete) and observation space design.
\item Explain the reward structure, emphasizing the components that encourage cooperation.
\end{itemize}
\item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
\item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
\item Define the evaluation metrics: average episode length and average reward.
\end{itemize}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

>>>>

% \author{Nicolò Malucelli}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{University of Bologna}
%   \streetaddress{Via dell'Università, 50}
%   \city{Cesena} 
%   \country{Italy}
% }
% \email{nicolo.malucelli@studio.unibo.it}

% \author{Davide Domini}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{University of Bologna}
%   \streetaddress{Via dell'Università, 50}
%   \city{Cesena} 
%   \country{Italy}
% }
% \email{davide.domini@unibo.it}

% \author{Gianluca Aguzzi}
% \affiliation{%
%   \institution{University of Bologna}
%   \streetaddress{Via dell'Università, 50}
%   \city{Cesena} 
%   \country{Italy}
% }
% \email{gianluca.aguzzi@unibo.it}

% \author{Mirko Viroli}
% \affiliation{%
%   \institution{University of Bologna}
%   \streetaddress{Via dell'Università, 50}
%   \city{Cesena} 
%   \country{Italy}
% }
% \email{mirko.viroli@unibo.it}

% % The default list of authors is too long for headers}
% \renewcommand{\shortauthors}{N. Malucelli et al.}

\author{Anonymous Author}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Anonymous university}
  \country{Anonymous location}
}
% \email{anonymous.author@studio.unibo.it}
\renewcommand{\shortauthors}{A. Author et al.}

\begin{abstract}
Multi-Agent Reinforcement Learning  is gaining popularity as a powerful extension of
  Single-Agent Reinforcement Learning for training collaborative or competitive agents
  in complex environments. 
%
MARL introduces unique challenges, such as non-stationarity, partial observability, 
  and credit assignment that complicate the learning process.  
%
Typically, in the literature, centralized training methods are used to tackle some of these challenges, 
  although they often face scalability limitations as the number of agents grows.
%
For this reason, decentralized training techniques have been proposed, however, 
  generally they have a longer convergence time compared to centralized ones 
  and may lead to instability.
%
This paper investigates the effectiveness of various neighbor-based decentralized training strategies 
  as a viable alternative to centralized training. 
%  
We evaluate Experience Sharing, Nearest Neighboring Averaging, and Nearest Neighboring Consensus methods 
  in a custom multi-agent environment and compare their performance against centralized training. 
%  
Our results show that neighbor-based methods can achieve comparable performance to centralized training 
  while offering improved scalability and communication efficiency. 
%
% Finally, we discuss the trade-offs between these methods and provide insights into their applicability 
%   in different scenarios.
\end{abstract}

%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

@@

\section{Neighboring-Based Distributed Learning Strategies}
\begin{itemize}
\item Provide a detailed explanation of each neighbor-based method:
\begin{itemize}
\item \textbf{Independent learners:} Emphasize its simplicity and scalability but highlight its vulnerability to non-stationarity.
\item \textbf{NN-Averaging:} Describe the weight averaging process, discuss the influence of neighbor selection and averaging frequency, and mention weighted averaging variations.
\item \textbf{NN-Consensus:} Explain the selection of the best-performing network and its potential benefits and drawbacks.
\item \textbf{Experience Sharing:} Detail how agents share experiences, discuss asynchronous vs. synchronous sharing, and highlight its advantages in sparse interaction environments.
\end{itemize}
\end{itemize}
\section{Experimental Setup}
\begin{itemize}
\item Introduce the custom "collect the items" multi-agent environment:
\begin{itemize}
\item Describe the environment's dynamics, agent goals, and challenges.
\item Specify the action space (continuous and discrete) and observation space design.
\item Explain the reward structure, emphasizing the components that encourage cooperation.
\end{itemize}
\item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
\item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
\item Define the evaluation metrics: average episode length and average reward.
\end{itemize}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography} 
\nocite{*}
